Hilbert space approximate Bayesian Gaussian processes using Stan

### 2020-03-24 Paper/manuscript_v2/manuscript_07_01.tex
improve dummy coding explanation

Due to the predictor \textit{sex} ($\bm{x}_2$) is a categorical variable ('1' for female and '2' for male), we can outline a multilevel model for the GP function, in a similar way like categorical effects are treated in linear models. The relative contribution of a GP function given one of the levels of the predictor (equation (\ref{ch5_eq_gpml2})) to a general mean GP function ($\mathcal{GP}(c + \bm{\beta}\bm{x}, k(\bm{x},\bm{x}', \theta_1))$ in  equation (\ref{ch5_eq_gpml1})) is defined. For the other level of the predictor, the GP function effects are set to zero (equation (\ref{ch5_eq_gpml2})). This multilevel construction is depicted as follows:
%
\begin{align} 
f(\bm{x}) &\sim \mathcal{GP}(c + \bm{\beta}\bm{x}, k(\bm{x},\bm{x}', \theta_1)) + g(\bm{x}), \label{ch5_eq_gpml1}
\end{align}

\noindent with
%
\begin{align} \label{ch5_eq_gpml2}
g(\bm{x}) =
\left\{
	\begin{array}{ll}
		0 & \;\; \mbox{if } \;\; x_2\!=\!\text{'}1\text{'}  \\
		\mathcal{GP}(c + \bm{\beta}\bm{x}, k(\bm{x},\bm{x}', \theta_2))  & \;\; \mbox{if } \;\; x_2\!=\!\text{'}2\text{'} 
	\end{array}.
\right.
\end{align}
%
%

@@

\noindent In the previous equations, $\theta_1$ contains the hyperparameters $\alpha_1$ and $\ell_1$ which are the marginal variance and lengthscale, respectively, of the general mean GP function, and $\theta_2$ contains the hyperparameters $\alpha_2$ and $\ell_2$ which are the marginal variance and lengthscale, respectively, of a specific GP function restricted to the male sex ($\bm{x}_2=\text{'}2\text{'}$).

>>>>

Due to the predictor \textit{sex} ($\bm{x}_2$) being a categorical variable ('1' for female and '2' for male), we apply dummy/treatment coding for the GP functions, in a similar way such coding is applied in linear models. A general mean GP function is defined for all observations, while a second GP function only applies to one of the predictor levels ('male' in this case) and is set to zero otherwise. More formally, this construction reads as follows:
%
\begin{align} 
f(\bm{x}) &\sim \mathcal{GP}(c + \bm{\beta}\bm{x}, k(\bm{x},\bm{x}', \theta_1)) + g(\bm{x}), \label{ch5_eq_gpml1}
\end{align}

\noindent with
%
\begin{align} \label{ch5_eq_gpml2}
g(\bm{x}) =
\left\{
	\begin{array}{ll}
		0 & \;\; \mbox{if } \;\; x_2\!=\!\text{'}1\text{'}  \\
		\mathcal{GP}(0, k(\bm{x},\bm{x}', \theta_2))  & \;\; \mbox{if } \;\; x_2\!=\!\text{'}2\text{'} 
	\end{array}
\right.
\end{align}
%
%

@@

\noindent In the former equations, $\theta_1$ contains the hyperparameters $\alpha_1$ and $\ell_1$ which are the marginal variance and lengthscale, respectively, of the general mean GP function, and $\theta_2$ contains the hyperparameters $\alpha_2$ and $\ell_2$ which are the marginal variance and lengthscale, respectively, of a specific GP function restricted to the male sex ($\bm{x}_2=\text{'}2\text{'}$).
